---
title: "tutorial for 'linreg'"
author: "Zhilin Zhang"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(linreg)
library(boot)
library(bench)
```

# linreg: Fitting Linear Models

## Description

`linreg` is used to fit linear models. It can be used to carry out regression with or without intercept and provide several hypothesis test results.

## Usage

linreg(y,x,method,intercept,CI_level)

### Arguments

#### y

A column vector, treated as outcome.

#### x

A numerical matrix, treated as predictor.

#### method

Character value, "qr" (by default), "svd" or "inverse"

a. [QR decompositiom methods](https://en.wikipedia.org/wiki/QR_decomposition)

b. [SVD decompositiom methods](https://en.wikipedia.org/wiki/Singular_value_decomposition)

c. [Least Squared estimator](https://en.wikipedia.org/wiki/Least_squares)

#### intercept

Logical values, TRUE (by default) or FALSE. If "TRUE", the model will include the intercept. 

#### CI_level

Numeric number, 0.95 (by default). Should be in (0,1) and directly change $\alpha$ used in confidence interval.

### Examples

*(1) Fit a simple linear regression model with intercept:*

```{r}
x <- rnorm(100)
y <- rnorm(100)
fit <- linreg(y,x)
```

*(2) Fit a simple linear regression model without intercept:*

```{r}
x <- rnorm(100)
y <- rnorm(100)
fit <- linreg(y,x,intercept = FALSE)
```

*(3) Fit a multiple linear regression model with intercept:*

```{r}
x <- rnorm(100)
y <- matrix(rnorm(600),nrow=100,ncol=6)
fit <- linreg(y,x)
```

*(4) Fit a multiple linear regression model without intercept:*

```{r}
x <- rnorm(100)
y <- matrix(rnorm(600),nrow=100,ncol=6)
fit <- linreg(y,x,intercept=FALSE)
```

*(4) Fit a multiple linear regression model with intercept and $\alpha=0.9$:*

```{r}
x <- rnorm(100)
y <- matrix(rnorm(600),nrow=100,ncol=6)
fit <- linreg(y,x,CI_level = 0.9)
```

we can check regression outcomes as follow:

a. check the exact fitted model

```{r}
fit$Call #function of the regression model
```

b. check estimated coefficients and the partial t test

```{r}
knitr::kable(fit$coefficients) 

#coefficients table include estimators of coefficients, standard error, confidence interval, T statistics and corresponding p-value.
```

c. check the fitted value of the model

```{r}
head(fit$fitted.values) #the first 6 fitted values
```

d. check the residuals

```{r}
fit$residuals # the first 6 residuals
```

e. check the model's mean square error

```{r}
fit$MSE
```

f. check the confidence interval of the estimator

```{r}
data.frame(fit$lower_ci,fit$upper_ci)
```

g. check the R^2 and adjusted R^2

```{r}
data.frame(fit$R_squared)
```

h. check the overall F test, results including f-statistics, corresponding p value and the degree of freedom.

```{r}
data.frame(fit$F_test)
```


## Correctness

We use aids in `boot` package to test the correctness and efficiency.

```{r}
head(aids)
```

```{r}
y <- aids$y
x <- as.matrix(aids[,c(2,3)])
linreg_fit <- linreg(y,x)
lm_fit <- lm(y~x)
summary_lm <- summary(lm_fit)
```

```{r}
# Testing Correctness:
all(c(all.equal(lm_fit$residuals, linreg_fit$residuals),
      all.equal(lm_fit$fitted.values, linreg_fit$fitted.values),
      all.equal(summary_lm$coefficients[[1]], linreg_fit$coefficients[[1]]),
      all.equal(summary_lm$coefficients[[2]], linreg_fit$coefficients[[2]]),
      all.equal(summary_lm$coefficients[[3]], linreg_fit$coefficients[[3]]),
      all.equal(summary_lm$coefficients[[4]], linreg_fit$coefficients[[4]]),
      all.equal(summary_lm$r.squared, linreg_fit$R_squared[[1]]),
      all.equal(summary_lm$adj.r.squared, linreg_fit$R_squared[[2]]),
      all.equal(summary_lm$fstatistic[[1]], linreg_fit$F_test[[1]])
    ))
```

The outcomes from two functions match, then we test the efficiency.

## Efficiency 

Compare two functions' efficiency using `bench:mark()` function:

```{r}
comparison_table1 <-  bench::mark(
linreg_qr = {
  beta.actual <-
    linreg(y, x)$coefficients[,1]
  as.vector(beta.actual)
},
linreg_svd = {
  beta.actual <-
    linreg(y, x,method="svd")$coefficients[,1]
  as.vector(beta.actual)
},
linreg_sinverse = {
  beta.actual <-
    linreg(y, x,method="inverse")$coefficients[,1]
  as.vector(beta.actual)
},
"stats::lm" = {
  beta.expected <- lm(y ~ x)$coefficients
  as.vector(beta.expected)
})  

summary(comparison_table1)

itr <- as.numeric(comparison_table1[[4]])
itr.ratio <- (itr-itr[4]) / itr[4]
```

From the results above, `linreg` with qr method is `r round(itr.ratio[1], digits = 2)` times faster than `stats::lm`, `linreg` with svd method is `r round(itr.ratio[2], digits = 2)` times faster than `stats::lm`,`linreg` use basic least square calculation is `r round(itr.ratio[3], digits = 2)` times faster than `stats::lm`.








